Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-24 manuscript/climate_sensitivity_draft.Rmd
Added sample text to final paragraph and added ref #120

As climate change drives increasing drought in many of the world's forests [@trenberth_global_2014; @intergovernmental_panel_on_climate_change_climate_2015], the fate of forests and their climate feedbacks will be shaped by the biophysical and physiological drivers observed here. 
Our results, consistent with other observations around the world, imply that the tallest, most exposed trees will be most affected [@bennett_larger_2015; @stovall_tree_2019]. 
We show that, at least within the mature forest studied here, the vulnerability conferred by tall height and associated crown exposure outweigh any advantage of a larger root system, even in drier microenvironments. 
This would suggest that the drought responses of trees in mature forests are more strongly differentiated along the size spectrum by their above- than below-ground environment. 
The same may not be true of systems where short trees exist outside of a buffered understory environment--*i.e.*, open grown trees or short-statured, early-successional forests.
The latter appear to be limited more strongly by root water access during drought [@bretfeld_plant_2018], and would also be dominated by species with different traits. 
The earlier-successional species at our site (*Liriodendron tulipifera*, *Quercus spp.*, *Fraxinus americana*) display a mix of traits conferring drought resistance (Table 2), while the late-successional *Fagus grandifolia* displayed high drought resistance, in part because it exists primarily within a buffered microenvironment. 
Further research on how leaf drought tolerance traits and drought vulnerability change over the course of succession would be valuable for addressing how drought resistance changes as forests age [e.g. @rodriguez-caton_long-term_2015]. 
In the meantime, the results of this study advance our knowledge of the factors conferring drought resistance in a mature forest, opening the door for more accurate forecasting of forest responses to future drought.

>>>>

As climate change drives increasing drought in many of the world's forests [@trenberth_global_2014; @intergovernmental_panel_on_climate_change_climate_2015], the fate of forests and their climate feedbacks will be shaped by the biophysical and physiological drivers observed here. 
Our results, consistent with other observations around the world, imply that the tallest, most exposed trees will be most affected [@bennett_larger_2015; @stovall_tree_2019]. 
We show that, at least within the mature forest studied here, the vulnerability conferred by tall height and associated crown exposure outweigh any advantage of a larger root system, even in drier microenvironments. 
This would suggest that the drought responses of trees in mature forests are more strongly differentiated along the size spectrum by their above- than below-ground environment. 
The same may not be true of systems where short trees exist outside of a buffered understory environment--*i.e.*, open grown trees or short-statured, early-successional forests.
The latter appear to be limited more strongly by root water access during drought [@bretfeld_plant_2018], and would also be dominated by species with different traits. 
The earlier-successional species at our site (*Liriodendron tulipifera*, *Quercus spp.*, *Fraxinus americana*) display a mix of traits conferring drought resistance (Table 2), while the late-successional *Fagus grandifolia* displayed high drought resistance, in part because it exists primarily within a buffered microenvironment. 
**This has potentially far-reaching implications for future forests. If we accept that climate change will cause more intense droughts, it is possible we will see a shift from mature forests with buffering, tall trees to forests with a shorter overall height (e.g.** see @mcdowell_pervasive_2020). **At this point, species that had high resistance due to buffering (such as F. grandifolia) may in turn become more susceptible. This shift, in addition to the susceptiblity of large trees to fire and pests/pathogens, could be highly detrimental to temperate forests. That being said,**
Further research on how leaf drought tolerance traits and drought vulnerability change over the course of succession would be valuable for addressing how drought resistance changes as forests age [e.g. @rodriguez-caton_long-term_2015]. 
In the meantime, the results of this study advance our knowledge of the factors conferring drought resistance in a mature forest, opening the door for more accurate forecasting of forest responses to future drought.
